Supplement

### 2023-03-02 06_Paper/ER-ED/ERED_Stage2/Supplement.Rmd
update supplement

``` {r SupplEffectER, echo=FALSE, message=FALSE, warning=FALSE} 
papaja::apa_table(
  SubjArousalReg_con,
  caption = "Post-hoc tests for effects of ER strategies on subjective arousal ratings.",
  escape = FALSE,
  placement = "H")

papaja::apa_table(
  EMGCorrReg_con,
  caption = "Post-hoc tests for effects of ER strategies on Corrugator activity",
  escape = FALSE,
  placement = "H")

papaja::apa_table(
  EMGLevReg_con,
  caption = "Post-hoc tests for effects of ER strategies on Levator activity",
  escape = FALSE,
  placement = "H")

>>>>

``` {r SupplEffectER, echo=FALSE, message=FALSE, warning=FALSE} 
papaja::apa_table(
  SubjArousalReg_con,
  caption = "Post-hoc tests for effects of ER strategies on subjective arousal ratings.",
  escape = FALSE,
  placement = "H"
  )

papaja::apa_table(
  EMGCorrReg_con,
  caption = "Post-hoc tests for effects of ER strategies on Corrugator activity",
  escape = FALSE,
  placement = "H"
  )

papaja::apa_table(
  EMGLevReg_con,
  caption = "Post-hoc tests for effects of ER strategies on Levator activity",
  escape = FALSE,
  placement = "H"
  )
